Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-15 ch04-lrmhinf/lrmhinf.tex
Some minor formatting things
Some formatting + OE figures

\chapter{Non-parametric Peak Modeling}
\label{sec:hinf}
\def\thisDir{ch04-lrmhinf}
\tikzsetfigurename{ch04fig}
\myEpigraph{Design is not just what it looks like and feels like. Design is how it works.}{Steve Jobs}{}
\researchBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
\glsresetall{}

@@

For mechatronic design and many other engineering disciplines it is important to obtain good  models that approximate the physical reality.
Recent trends in many disciplines have led to increasingly complicated systems.
Consequently, building a full-complexity parametric model rapidly becomes disproportionately expensive for a required model fidelity.
Often, such parametric models are required to understand elementary properties of the system such as the resonance frequencies, damping of different poles, the maximal gain of the system.
In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system.
This is a problem that is important in the design of robust controllers~\citep{Oomen2016} to characterize the effect of unmodeled dynamics in low-complexity models used for control.
Such analysis allows one to verify that the eventually designed controller stabilizes the system.

@@

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Traditional set-up.}  
    \label{fig:lrmhinf:vibration-isolation:traditional}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Principle of sky-hook damping.}  
    \label{fig:lrmhinf:vibration-isolation:skyhook}
  \end{subfigure}
  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
  \caption[Vibration isolation set-ups (traditional, sky-hook damping)]{Conceptual illustration of (active) vibration isolation set-ups. 
  In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
  % If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
  % When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
  }
  \label{fig:lrmhinf:vibration-isolation}
\end{figure}

>>>>

\chapter{Non-parametric Peak Modeling}
\label{sec:hinf}
\chapterBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
\def\thisDir{ch04-lrmhinf}
\tikzsetfigurename{ch04fig}
\myEpigraph{Design is not just what it looks like and feels like. Design is how it works.}{Steve Jobs}{}
\glsresetall{}

@@

\section{Introduction}
\label{sec:lrmhinf:intro}
For mechatronic design and many other engineering disciplines it is important to obtain good  models that approximate the physical reality.
Recent trends in many disciplines have led to increasingly complicated systems.
Consequently, building a full-complexity parametric model rapidly becomes disproportionately expensive for a required model fidelity.
Often, such parametric models are required to understand elementary properties of the system such as the resonance frequencies, damping of different poles, the maximal gain of the system.
In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system.
This is a problem that is important in the design of robust controllers~\citep{Oomen2016} to characterize the effect of unmodeled dynamics in low-complexity models used for control.
Such analysis allows one to verify that the eventually designed controller stabilizes the system.

@@

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
   \centering
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Traditional set-up.}  
    \label{fig:lrmhinf:vibration-isolation:traditional}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Principle of sky-hook damping.}  
    \label{fig:lrmhinf:vibration-isolation:skyhook}
  \end{subfigure}
  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
  \caption[Vibration isolation set-ups (traditional, sky-hook damping)]{Conceptual illustration of (active) vibration isolation set-ups. 
  In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
  % If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
  % When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
  }
  \label{fig:lrmhinf:vibration-isolation}
\end{figure}
